---
title: "wk9-homework-Jewell-Carl"
author: "Carl Jewell"
date: "November 16, 2015"
output: html_document
---

#### 1. Initial GitHub workflow

a. Pat yourselves on the back if you were able to "fork", then "clone" this repo. Maybe massage your brain, too.

b. Re-save this file with your last and first name as well as altering the title of this file.

#### Tips for creating functions

*Use the least possible number of steps. Work line by line, printing out each value as you create the function. Trying to create a function that will solve the whole problem will typically lead to long debugging times because you will not know where you made the mistake.*

#### 2. if-then-else
Create a function `is.a.number()` that takes a single parameter `X` and returns `"Is a number"` if it is a number, `"Is NA"` if it is an `NA` value, and `"I have no clue"` if it is neither a number nor an `NA` value. Use the `is.na()` and `is.numeric()` functions.

```{r}
is.a.number <- function(X) {

if (is.numeric(X) == 'TRUE'){
something <- "Is a number"
} else {
if (is.na(X) == 'TRUE'){
something <- "Is NA"
} else {
something <- "I have no clue"
}
}
return(something)
}
```

#### 3. primes 
Create a function that when inputting a single prime number between 3 and 100, it will output a `TRUE` or `FALSE` in a `message()`. Insert an error message as if somebody were to insert a number less than 3, greater than 100, or a non-numeric character. (*Please don't insert all of the prime numbers between 3 and 100 into the function...*)

```{r}
is.prime <- function(X){
if ( X %% 2 == 0) { 
something <- 'False'
} else {
if ( X %% 3 == 0) {
something <- 'False'
} else { 
something <- 'True'
}
}
return(something)
}
```

#### 4. ggplot2

a. Using `ggplot2`, create a function that when inputting a single continuous variable, it will print out a histogram. Include arguments to alter the theme, x-variable label, a title, and a `TRUE` or `FALSE` option to create a density plot.

```{r}
library(ggplot2)

new.histogram <- function(dat, theme1, xlab1, title1, density_option) {
  if (density_option == 'TRUE') {
  
  if (theme1 == 'theme_bw'){plot <- ggplot(dat, aes(x = data)) + geom_histogram() + labs(title = title1) + labs(x = xlab1) + theme_bw() + geom_density()}
    
  if (theme1 == 'theme_grey'){plot <- ggplot(dat, aes(x = data)) + geom_histogram() + labs(title = title1) + labs(x = xlab1) + theme_grey() + geom_density()}
  if (theme1 == 'theme_blank'){plot <- ggplot(dat, aes(x = data)) + geom_histogram() + labs(title = title1) + labs(x = xlab1) + theme_blank() + geom_density()}
  if (theme1 == 'theme_classic'){plot <- ggplot(dat, aes(x = data)) + geom_histogram() + labs(title = title1) + labs(x = xlab1) + theme_classic() + geom_density()}
  if (theme1 == 'theme_minimal'){plot <- ggplot(dat, aes(x = data)) + geom_histogram() + labs(title = title1) + labs(x = xlab1) + theme_minimal() + geom_density()}
  } else {
      if (theme1 == 'theme_bw'){plot <- ggplot(dat, aes(x = data)) + geom_histogram() + labs(title = title1) + labs(x = xlab1) + theme_bw() + geom_density()}
    
  if (theme1 == 'theme_grey'){plot <- ggplot(dat, aes(x = data)) + geom_histogram() + labs(title = title1) + labs(x = xlab1) + theme_grey()}
  if (theme1 == 'theme_blank'){plot <- ggplot(dat, aes(x = data)) + geom_histogram() + labs(title = title1) + labs(x = xlab1) + theme_blank()}
  if (theme1 == 'theme_classic'){plot <- ggplot(dat, aes(x = data)) + geom_histogram() + labs(title = title1) + labs(x = xlab1) + theme_classic()}
  if (theme1 == 'theme_minimal'){plot <- ggplot(dat, aes(x = data)) + geom_histogram() + labs(title = title1) + labs(x = xlab1) + theme_minimal()}
  }
  
  return(plot)
}

```


b. Similarly, create a function that when inputting two continuous variables, it will print a scatterplot. Additionally, in the console, print the mean and variance of the two variables as well as the coefficient value of the specified x-variable.  Include arguments to alter the title and a `TRUE` or `FALSE` option to include a smoothing method of *lm* aka a simple linear model line in/on the scatterplot.

```{r}

```


#### 5. Remaining GitHub workflow

a. Now finish off the workflow of submitting your homework by "committing" the changes locally, "pushing" the changes to YOUR online repo, and finally creating a pull request. 

b. Pat yourselves on the back, again.  You deserved it.
